### 2024-06-16 Reports/Progress Report/sections/method.tex
added diagram for methodology overview

Our study uses survey responses from the European Social Survey (ESS) related to political interests and socio-political orientations to predict party affiliations within the same survey. We employ two models: the first model processes survey responses for input questions and generates \textit{Statements}, which are normal human-like speeches rather than discrete survey numbers. The second model uses these statements to predict party affiliations by analyzing what someone who made those statements might think about the target survey question. We evaluate the performance by employing accuracy metrics, using ESS data as the gold standard.

@@

>>>>

Our study uses survey responses from the European Social Survey (ESS) related to political interests and socio-political orientations to predict party affiliations within the same survey. We employ two models: the first model processes survey responses for input variables and generates \textit{Statements}, which are normal human-like speeches rather than discrete survey numbers. The second model uses these statements to predict party affiliations by analyzing what someone who made those statements might think about the target survey variable. We evaluate the performance by employing accuracy metrics, using ESS data as the gold standard.

@@

\include{figures/method_overview}
